Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images

### 2016-02-29 ms.tex
minor edits

To coadd the W1/W2 single exposures, we make use of the \cite{lang14}
unWISE coaddition framework, and perform our image processing with an 
adaptation of the codebase from that work. We briefly mention
a few of the salient aspects of the unWISE coaddition methodology here; for
a full discussion see \cite{lang14}.

% mention that we use the same tile centers as Atlas and original unWISE
Like the official WISE Atlas coadds, unWISE processing divides the sky
into a set of 18240 $\sim$1.5$^{\circ}$$\times$$\sim$1.5$^{\circ}$ tiles
arranged along iso-declination rings. Unlike the Atlas tiles, the
unWISE code uses Lanczos interpolation to preserve the native WISE 
angular resolution during coaddition, creating stacked outputs which are 2048 
pixels on a side, with pixels of size 2.75$''$.

@@

\begin{itemize}
\item We include all publicly available NEOWISER W1 and W2 exposures, 
approximately doubling the number of input L1b frames relative to \cite{lang14}.
\item We adopt custom zero points based on repeat photometry at the ecliptic 
poles. In contrast, the \cite{lang14} unWISE processing adopted zero points 
based on the L1b header metadata.
\item We explicitly reject exposures contaminated by the Moon and/or solar 
system planets. No such rejection was included in the \cite{lang14} unWISE 
W1/W2 coadds, although these and other artifacts were addressed to some extent 
via general-purpose outlier rejection.
\item In this work we attempt to recover Moon-affected frames by applying 
polynomial background level corrections to the contaminated exposures.
\end{itemize}

The outputs generated in this work follow the same data model as those of 
\cite{lang14}. For each tile, a stacked image is created, plus auxiliary
maps of useful quantities such as the per-pixel inverse variance and integer 
coverage. Like those of \cite{lang14}, our coadds have units of Vega 
nanomaggies.

@@

Although we were able to dramatically reduce the impact of Moon contamination
on our coadds with the exposure rejection procedure of $\S$\ref{sec:moon},
we would ideally like to recover as much Moon-contaminated data as possible,
rather than simply discard it all outright. To that end, we have added an 
after-burner step to our coaddition procedure which attempts to salvage those 
frames which were flagged with \verb|MOON_MASKED| and displayed abnormally 
large pixel value standard deviations. The procedure we employ is a variant of 
that described in $\S6.4.1$ of \cite{meisner14}.

@@

Figures 4 and 5 show large-scale renderings of our full-depth coadds 
over the north and south Galactic caps respectively. It is 
apparent that the Moon contamination has been completely eliminated in
W1 and dramatically reduced in W2. It is possible that simply folding in 
additional NEOWISER W2 frames from forthcoming data releases will diminish the 
remaining Moon imprint to such an extent that no additional processing 
modifications will be required to address this issue.

\begin{figure*} [ht]
 \begin{center}
  \epsfig{file=w2_large_scale.eps, width=7.0in}
  \caption{\label{fig:w2_large} A large portion of the south Galactic
           cap near the ecliptic plane is shown in W2. Top: \cite{lang14}
           unWISE coadds based on the AllWISE release imaging and without
           rejection of Moon-contaminated frames. Bottom: same region of
           sky in our new AllWISE+NEOWISER stacks, with double the
           redundancy in sky coverage and rejection/recovery of 
           Moon-contaminated frames.}
 \end{center}
\end{figure*}
% should state approximate bounding coords in terms of lambda, beta

>>>>

To stack the W1/W2 single exposures, we make use of the \cite{lang14}
unWISE coaddition framework, and perform our image processing with an 
adaptation of the codebase from that work. We briefly mention
a few of the salient aspects of the unWISE coaddition methodology here; for
a full discussion see \cite{lang14}.

% mention that we use the same tile centers as Atlas and original unWISE
Like the official WISE Atlas coadds, unWISE processing divides the sky
into a set of 18240 $\sim$1.5$^{\circ}$$\times$$\sim$1.5$^{\circ}$ tiles
arranged along iso-declination rings. Unlike the Atlas stacks, the
unWISE code uses Lanczos interpolation to preserve the native WISE 
angular resolution during coaddition, creating stacked outputs which are 2048 
pixels on a side, with 2.75$''$ pixels.

@@

\begin{itemize}
\item We include all publicly available NEOWISER W1 and W2 exposures, 
approximately doubling the number of input L1b frames relative to the 
\cite{lang14} processing.
\item We adopt custom zero points based on repeat photometry at the ecliptic 
poles. In contrast, the \cite{lang14} unWISE processing adopted zero points 
based on the L1b header metadata.
\item We explicitly reject exposures contaminated by the Moon and/or solar 
system planets. No such rejection was included in the \cite{lang14} unWISE 
W1/W2 coadds, although these and other artifacts were addressed to some extent 
via general-purpose outlier rejection.
\item In this work we attempt to recover Moon-affected frames by applying 
polynomial background level corrections to the contaminated exposures.
\end{itemize}

The outputs generated in this work follow the same data model as those of 
\cite{lang14}. For each tile, a stacked intensity image is created, as well as
auxiliary maps of useful quantities such as the per-pixel inverse variance and
integer coverage. Like those of \cite{lang14}, our coadds have units of Vega 
nanomaggies.

@@

Although we are able to dramatically reduce the impact of Moon contamination
on our coadds with the exposure rejection procedure of $\S$\ref{sec:moon},
we would ideally like to recover as much Moon-contaminated data as possible,
rather than simply discard it all outright. To that end, we have added an 
after-burner step to our coaddition procedure which attempts to salvage those 
frames which were flagged with \verb|MOON_MASKED| and displayed abnormally 
large pixel value standard deviations. The procedure we employ is a variant of 
that described in $\S6.4.1$ of \cite{meisner14}.

@@

Figures \ref{fig:w2_large} and 5 show large-scale renderings of our full-depth 
coadds over the north and south Galactic caps respectively. It is 
apparent that the Moon contamination has been completely eliminated in
W1 and dramatically reduced in W2. It is possible that simply folding in 
additional NEOWISER W2 frames from forthcoming data releases will diminish the 
remaining Moon imprint to such an extent that no additional processing 
modifications will be required to address this issue.

\begin{figure*} [ht]
 \begin{center}
  \epsfig{file=w2_large_scale.eps, width=7.0in}
  \caption{\label{fig:w2_large} A large portion of the south Galactic
           cap near the ecliptic plane is shown in W2. Top: \cite{lang14}
           unWISE coadds based on the AllWISE release imaging and without
           rejection of Moon-contaminated frames. Bottom: same region of
           sky in our new AllWISE+NEOWISER stacks, with double the
           redundancy in sky coverage and rejection/recovery of 
           Moon-contaminated frames. It is clear that the scattered
           moonlight has been largely removed in W2, although 
           some traces still remain.}
 \end{center}
\end{figure*}
% should state approximate bounding coords in terms of lambda, beta
